---
title: "Crowdsourced Cyclospora Watch"
output:
  html_document:
    theme: flatly
    toc: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

required_pkgs <- c("googlesheets4", "dplyr", "tidyr", "stringr", "lubridate",
                    "ggplot2", "janitor", "purrr", "knitr", "DT", "httr2", "jsonlite", "maps")
new_pkgs <- required_pkgs[!(required_pkgs %in% installed.packages()[, "Package"])]
if (length(new_pkgs)) install.packages(new_pkgs)
library(googlesheets4); library(dplyr); library(tidyr); library(stringr)
library(lubridate); library(ggplot2); library(janitor); library(purrr)
library(knitr); library(DT)

## Shared vocabulary rules, sourced rather than duplicated into both entry
## points. assert_utf8_locale() runs before any text is read: under a non-UTF-8
## locale normalize_punct() silently does nothing, and every curly apostrophe
## forks a duplicate category.
source("R/vocabulary-integrity.R")
assert_utf8_locale()
```

```{r config}
# ---- EDIT THIS SECTION FOR YOUR FORM ----
SHEET_URL <- "https://docs.google.com/spreadsheets/d/1n1VJ99Ko7mvFQmKRX_QrFLFFziMAGKpkUNmK40QxLpU/edit?usp=sharing"
gs4_deauth()

col_signatures <- c(
  timestamp        = "^timestamp$",
  consent          = "consent",
  state            = "what state",
  why_believe      = "why do you believe",
  produce_checklist = "did you eat any of the following",
  produce_other    = "anything else you remember eating",
  shop_raw         = "shop.?dine",
  duration         = "how long did symptoms last",
  onset_date       = "when did symptoms start"
)

match_columns <- function(actual_names, signatures) {
  matched <- vapply(signatures, function(sig) {
    hits <- actual_names[str_detect(str_to_lower(actual_names), str_to_lower(sig))]
    if (length(hits) == 0) NA_character_ else hits[1]
  }, character(1))
  matched[!is.na(matched)]
}

# Seed dictionaries - starting point + offline fallback only. The real,
# growing vocabulary lives in category_vocabulary.json (see below).
produce_dict_seed <- list(
  # Lettuce is split into whole-head vs prepackaged/bagged - this
  # distinction matters a lot for traceback (prepackaged/bagged salad is
  # the recurring outbreak vehicle, whole heads much less so), so we keep
  # them as separate categories rather than merging into one "lettuce".
  romaine_head        = "romaine.*head|head.*romaine|whole romaine",
  romaine_prepackaged = "romaine.*(prepackag|bagged)|bagged romaine",
  iceberg_head        = "iceberg.*head|head.*iceberg|whole iceberg",
  iceberg_prepackaged = "iceberg.*(prepackag|bagged)|bagged iceberg",
  mesclun_spring_mix  = "mesclun|spring mix",
  spinach = "spinach", cilantro = "cilantro|coriander", basil = "\\bbasil\\b",
  parsley = "parsley", raspberries = "raspberr", strawberries = "strawberr",
  blackberries = "blackberr", cucumber = "cucumber", tomato = "tomato",
  snap_peas = "snap pea|sugar snap", green_onion = "green onion|scallion|spring onion",
  cabbage = "cabbage|slaw", carrot = "carrot", broccoli = "broccoli",
  melon = "cantaloupe|honeydew|melon", bell_pepper = "bell pepper|sweet pepper",
  avocado = "avocado|guacamole", celery = "celery", cauliflower = "cauliflower",
  dill = "\\bdill\\b", radish = "radish",
  mint = "\\bmint\\b",
  # Generic bagged/premade salad where the specific lettuce type isn't
  # named - catches free-text synonyms like "premade salad", "pre-made
  # side salad", "grab and go salad" so they land here instead of
  # spawning a near-duplicate category.
  salad_bagged = "bagged salad|salad kit|salad mix|premade salad|pre-made salad|pre made salad|ready.to.eat salad|grab.and.go salad",
  salad_restaurant = "restaurant salad|salad bar"
)

store_dict_seed <- list(
  kroger = "kroger", trader_joes = "trader joe", whole_foods = "whole foods",
  walmart = "wal[- ]?mart", target = "\\btarget\\b", publix = "publix",
  aldi = "aldi", costco = "costco", safeway = "safeway", wegmans = "wegmans",
  taco_bell = "taco bell", chipotle = "chipotle", subway = "subway",
  mcdonalds = "mcdonald", local_farmers_market = "farmers?[- ]?market",
  local_restaurant = "^restaurant$|local restaurant"
)

baseline_commonness_seed <- c(
  # Old single "lettuce" baseline (55) split across the new granular
  # categories - rough guesses, tune as you like.
  romaine_head = 15, romaine_prepackaged = 20, iceberg_head = 10,
  iceberg_prepackaged = 12, mesclun_spring_mix = 8,
  spinach = 25, cilantro = 20, basil = 10, parsley = 12,
  raspberries = 10, strawberries = 30, blackberries = 8, cucumber = 30,
  tomato = 45, snap_peas = 8, green_onion = 20, cabbage = 15, carrot = 40,
  broccoli = 35, melon = 20, bell_pepper = 30, avocado = 35, celery = 15,
  cauliflower = 15, dill = 8,
  radish = 6, mint = 5, salad_bagged = 25, salad_restaurant = 20
)

VOCAB_PATH <- "category_vocabulary.json"

# Reads the vocabulary file, or returns NULL if it genuinely doesn't exist
# yet (first run). A file that EXISTS but won't parse is a hard error: the
# old behaviour returned NULL there, which silently rebuilt the vocabulary
# from seed values and then overwrote every accumulated category, baseline
# and cached classification with that skeleton.
read_vocabulary_file <- function(path) {
  if (!file.exists(path)) return(NULL)
  tryCatch(
    jsonlite::fromJSON(path, simplifyVector = TRUE),
    error = function(e) {
      stop(
        path, " exists but could not be parsed: ", conditionMessage(e), "\n",
        "  Refusing to continue. Proceeding would rebuild the vocabulary from seed\n",
        "  values and overwrite every accumulated category, baseline and cached\n",
        "  classification. Restore it with `git checkout -- ", path, "` or repair\n",
        "  the file by hand, then re-run.",
        call. = FALSE
      )
    }
  )
}

# as.list() on a possibly-absent JSON field, without inventing a value.
as_list_or_empty <- function(x) if (is.null(x)) list() else as.list(x)

load_vocabulary <- function(path, seed_produce, seed_store, seed_baseline) {
  v <- read_vocabulary_file(path)
  list(
    produce_categories = union(if (!is.null(v)) v$produce_categories else character(0), seed_produce),
    store_categories   = union(if (!is.null(v)) v$store_categories else character(0), seed_store),
    baseline_commonness = modifyList(
      as.list(seed_baseline),
      if (!is.null(v) && !is.null(v$baseline_commonness)) as.list(v$baseline_commonness) else list()
    ),
    # PERSISTENT CLASSIFICATION CACHE - locks in each specific raw phrase's
    # decision forever, so already-classified responses can't silently
    # drift to a different category on a later run.
    produce_item_map = if (!is.null(v) && !is.null(v$produce_item_map)) as.list(v$produce_item_map) else list(),
    store_item_map    = if (!is.null(v) && !is.null(v$store_item_map)) as.list(v$store_item_map) else list(),
    # PROVENANCE for each baseline. Parallel maps rather than nesting inside
    # baseline_commonness, because that field is read as a flat named vector
    # by the signal-ratio code and changing its shape would break the metric.
    # baseline_source: "USDA ERS Food Availability" | "author_estimate"
    # baseline_confidence: "exact_match" | "unsourced"
    baseline_source     = if (!is.null(v) && !is.null(v$baseline_source)) as.list(v$baseline_source) else list(),
    baseline_confidence = if (!is.null(v) && !is.null(v$baseline_confidence)) as.list(v$baseline_confidence) else list(),
    # CATEGORY provenance (distinct from the BASELINE provenance above).
    # Must be loaded, not just carried over on save: stamp_category_provenance()
    # below adds to these, and if they arrived empty the save-time merge would
    # treat the partial in-memory copy as authoritative and drop the rest.
    category_source_type      = if (!is.null(v) && !is.null(v$category_source_type)) as.list(v$category_source_type) else list(),
    active_since_form_version = if (!is.null(v) && !is.null(v$active_since_form_version)) as.list(v$active_since_form_version) else list(),
    checklist_label           = if (!is.null(v) && !is.null(v$checklist_label)) as.list(v$checklist_label) else list(),
    category_notes            = if (!is.null(v) && !is.null(v$category_notes)) as.list(v$category_notes) else list()
  )
}

## Stamps provenance on any category that lacks it.
##
## Deliberately here rather than inside classify_and_grow(): categories can
## enter the vocabulary by several routes - the LLM minting a new one, the
## checklist union, a hand edit to the file - and only a sweep catches all of
## them. Existing labels are never overwritten, so this is purely additive and
## self-healing. Without it the provenance fields go stale the first time
## anyone reports a new food or store, which is exactly what happened to the
## 16 categories added after the initial backfill.
stamp_category_provenance <- function(vocab, checklist_categories = character(0)) {
  allc <- c(vocab$produce_categories, vocab$store_categories)
  for (cat in setdiff(allc, names(vocab$category_source_type))) {
    vocab$category_source_type[[cat]] <-
      if (cat %in% checklist_categories) "checklist_direct" else "freetext_classified"
  }
  for (cat in setdiff(allc, names(vocab$active_since_form_version))) {
    vocab$active_since_form_version[[cat]] <- "v1"
  }
  vocab
}

# MERGE-ON-WRITE, not clobber-on-write.
#
# `vocab` is a snapshot taken when this run started. Another writer - the
# hourly Action, or someone running the analysis script locally - may have
# added entries since. Serializing the snapshot over the whole file would
# silently discard them, with no conflict, because a full-file overwrite
# always wins a rebase.
#
# So: re-read the file we are about to replace and merge into it. A side
# effect worth stating, because it is the main safety property here: a
# caller that loaded only PART of the file (e.g. a script whose
# load_vocabulary() never reads the item maps) can no longer destroy the
# keys it never looked at.
save_vocabulary <- function(vocab, path) {
  on_disk <- read_vocabulary_file(path)
  merged <- vocab

  if (!is.null(on_disk)) {
    # Carry over any top-level key this function doesn't explicitly manage.
    # Without this, a field added to the file (by hand, by a tool, or by a
    # newer version of this script) is silently dropped the next time any
    # run saves - which is exactly how the item maps used to get wiped.
    for (k in setdiff(names(on_disk), names(merged))) merged[[k]] <- on_disk[[k]]

    # Categories are additive - keep both sides.
    merged$produce_categories <- union(vocab$produce_categories, on_disk$produce_categories)
    merged$store_categories   <- union(vocab$store_categories,   on_disk$store_categories)

    # For per-key maps, the on-disk value wins. modifyList(a, b) gives `b`
    # precedence, so passing on_disk second means an entry already written
    # by someone else survives, while genuinely new keys from this run are
    # still added. On-disk decisions are the earlier, possibly already
    # published ones, and neither script ever edits these in memory.
    merged$baseline_commonness <- modifyList(
      as_list_or_empty(vocab$baseline_commonness), as_list_or_empty(on_disk$baseline_commonness))
    merged$produce_item_map <- modifyList(
      as_list_or_empty(vocab$produce_item_map), as_list_or_empty(on_disk$produce_item_map))
    merged$store_item_map <- modifyList(
      as_list_or_empty(vocab$store_item_map), as_list_or_empty(on_disk$store_item_map))
    merged$baseline_source <- modifyList(
      as_list_or_empty(vocab$baseline_source), as_list_or_empty(on_disk$baseline_source))
    merged$baseline_confidence <- modifyList(
      as_list_or_empty(vocab$baseline_confidence), as_list_or_empty(on_disk$baseline_confidence))
    # Same direction as the maps above: on-disk wins for keys both sides have,
    # while categories stamped for the first time in this run are kept.
    for (k in c("category_source_type", "active_since_form_version",
                "checklist_label", "category_notes")) {
      merged[[k]] <- modifyList(as_list_or_empty(vocab[[k]]), as_list_or_empty(on_disk[[k]]))
    }
  }

  # ATOMIC WRITE. write_json() straight onto `path` leaves a truncated file
  # if the process dies mid-write, and a truncated file is exactly what
  # read_vocabulary_file() now refuses to load. Write to a tempfile in the
  # SAME directory (so rename stays on one filesystem and is atomic), then
  # rename over the target. A killed process can leave a stray temp file,
  # but never a partial category_vocabulary.json.
  tmp <- tempfile(pattern = ".category_vocabulary", tmpdir = dirname(path), fileext = ".json")
  jsonlite::write_json(merged, tmp, auto_unbox = TRUE, pretty = TRUE)
  if (!file.rename(tmp, path)) {
    unlink(tmp)
    stop("Could not atomically replace ", path, call. = FALSE)
  }
  invisible(merged)
}
```

```{r functions}
## Canonicalise typographic punctuation to ASCII before anything else reads
## the string. Curly apostrophes were the single largest source of poisoned
## categories (13 of 36) and the most likely trigger for LLM key-drift: a
## phrase sent as a JSON key containing U+2019 can come back with U+0027,
## the exact-name lookup misses, and the item falls to the regex fallback.
## Applied at ingestion so tokenisation, caching and the API call all see
## the same canonical form.
normalize_punct <- function(x) {
  x <- gsub("[‘’ʼ′´]", "'", x, perl = TRUE)
  x <- gsub("[“”″]", '"', x, perl = TRUE)
  x <- gsub("[‐‑‒–—]", "-", x, perl = TRUE)
  x <- gsub(" ", " ", x, perl = TRUE)
  x
}

## Split on , ; and newline - but NOT inside parentheses. Respondents write
## "Agawam Diner (Rowley, MA); Campfire Grille (Bridgton, ME)", and a plain
## comma split turned that one answer into three junk categories including
## the fragments "Ma); Campfire Grille (Bridgton" and "Me)". Newlines matter
## too: one response listed seven businesses on seven lines and produced a
## single category containing all of them.
split_delims <- function(s) {
  if (is.na(s) || !nzchar(s)) return(character(0))
  ch <- strsplit(s, "", fixed = TRUE)[[1]]
  depth <- 0L; cur <- character(0); out <- character(0)
  for (c in ch) {
    if (c == "(") depth <- depth + 1L
    else if (c == ")") depth <- max(0L, depth - 1L)
    if (depth == 0L && (c == "," || c == ";" || c == "\n")) {
      out <- c(out, paste0(cur, collapse = "")); cur <- character(0)
    } else cur <- c(cur, c)
  }
  c(out, paste0(cur, collapse = ""))
}

## Declining to answer is not a food. Nine responses answer the produce
## free-text with a negation; before this filter they reached the classifier
## and could become categories like "No. I Made Sure To Not :(". Dropped
## here means never classified and never cached. The \\b guards keep real
## foods that merely start with these letters - "nopales", "nectarines".
NEGATION_RE <- paste0(
  "^(no|nope|none|nothing|n/?a|na|nil|never|not really|not that i|",
  "i don'?t|i do not|unsure|unknown|idk|[-.–]+)\\b|^[-.–[:space:]]*$")
is_negation <- function(item) {
  it <- str_squish(str_to_lower(item))
  !nzchar(it) | str_detect(it, NEGATION_RE)
}

split_freetext <- function(raw_text_vec) {
  tibble(row_id = seq_along(raw_text_vec), raw = raw_text_vec) %>%
    filter(!is.na(raw), str_trim(raw) != "") %>%
    mutate(raw = normalize_punct(raw)) %>%
    mutate(parts = map(raw, split_delims)) %>%
    select(row_id, parts) %>%
    unnest(parts) %>%
    mutate(item = str_squish(str_to_lower(parts))) %>%
    filter(item != "", !is_negation(item)) %>%
    select(row_id, item)
}

## ---- CHECKLIST ROUTING ---------------------------------------------------
## Checklist answers are preset option strings - already category-shaped and
## unambiguous - so they resolve by direct lookup and never reach the LLM or
## the regex fallback. That removes the whole class of drift for ~90% of the
## reported volume, and leaves the classifier to do the one job it's needed
## for: messy free text.
CHECKLIST_MAP_PATH <- "checklist-mapping.json"

checklist_map <- local({
  if (!file.exists(CHECKLIST_MAP_PATH)) {
    stop(CHECKLIST_MAP_PATH, " is missing - checklist answers cannot be routed. ",
         "Refusing to fall back to the classifier, which would silently re-introduce ",
         "drift on the highest-volume field.", call. = FALSE)
  }
  m <- jsonlite::fromJSON(CHECKLIST_MAP_PATH, simplifyVector = FALSE)$mapping
  if (is.null(m) || length(m) == 0) stop(CHECKLIST_MAP_PATH, " has no 'mapping' object.", call. = FALSE)
  m
})

## Resolves checklist text to categories. An option present in the form but
## absent from the map is a hard error, not a guess - a new checklist option
## must be mapped by hand or the counts silently lose it.
classify_checklist <- function(raw_text_vec) {
  long <- split_freetext(raw_text_vec)
  if (nrow(long) == 0) return(long %>% mutate(category = character(0)))
  unknown <- setdiff(unique(long$item), names(checklist_map))
  if (length(unknown)) {
    stop("checklist option(s) not present in ", CHECKLIST_MAP_PATH, ":\n  - ",
         paste(unknown, collapse = "\n  - "),
         "\n  Add them to the mapping (with the category slug they belong to) and re-run.",
         call. = FALSE)
  }
  long %>% mutate(category = vapply(item, function(i) as.character(checklist_map[[i]]), character(1)))
}

regex_classify <- function(item, dict) {
  hit <- names(dict)[map_lgl(dict, ~ str_detect(item, .x))]
  # No seed pattern matched. Return NA rather than str_to_title(item):
  # echoing the respondent's raw text back as a category name is how
  # entries like "No. I Made Sure To Not :(" and "Bibb Lettuce Head"
  # became permanent categories. NA means "undecided this run" - the
  # item is left uncategorized and retried next run, when the LLM may
  # well be reachable again.
  if (length(hit) == 0) return(NA_character_)
  hit[1]
}

# Categories only ever enter the vocabulary from a real decision.
# NA means undecided, so it must never be unioned in.
merge_categories <- function(known_categories, mapping) {
  union(known_categories, unique(mapping[!is.na(mapping)]))
}

# LLM does the primary classification and grows the category vocabulary -
# reuses existing categories where they fit, mints new lowercase_snake_case
# ones for genuinely new foods instead of dumping them in "other". Falls
# back to regex automatically if the API call fails.
CLASSIFICATION_METHOD <- "llm"   # "llm" or "regex"

call_claude_classify_dynamic <- function(items, known_categories, domain = c("produce", "store"),
                                          api_key = Sys.getenv("ANTHROPIC_API_KEY"),
                                          model = "claude-haiku-4-5-20251001") {
  domain <- match.arg(domain)
  if (identical(api_key, "") || length(items) == 0) return(NULL)

  domain_instructions <- if (domain == "produce") {
    paste0(
      "1. If it clearly matches an EXISTING category, use that EXACT category name - do not ",
      "create a near-duplicate or synonym (e.g. don't make \"fresh_cilantro\" if \"cilantro\" ",
      "already exists, or \"pre_made_salad\" if \"salad_bagged\" already exists - these describe ",
      "the same thing).\n",
      "2. For lettuce/salad specifically, PRESERVE the distinction between whole-head produce ",
      "(e.g. \"romaine_head\", \"iceberg_head\") and prepackaged/bagged forms (e.g. ",
      "\"romaine_prepackaged\", \"iceberg_prepackaged\", \"salad_bagged\") when the respondent's ",
      "answer indicates which form it was - this distinction matters for outbreak traceback. If ",
      "the form isn't specified and it's a generic mixed salad, use the existing generic ",
      "\"salad_bagged\" category rather than inventing a new one.\n",
      "3. If it genuinely doesn't fit any existing category, invent ONE new concise category ",
      "name in lowercase_snake_case (1-3 words, e.g. \"purslane\" or \"bean_sprouts\") that ",
      "could sensibly apply to future similar items too. Do NOT use \"other\" - always pick or ",
      "create a real, specific category.\n",
      "4. If multiple items in this batch describe the same new food, give them the SAME new ",
      "category name.\n"
    )
  } else {
    paste0(
      "1. Your ONLY job is to normalize SPELLING/PHRASING variants of the SAME specific named ",
      "place into one category (e.g. \"Krogers\", \"the kroger on main\", \"kroger grocery\" all ",
      "become \"kroger\"). If an EXISTING category is clearly the same specific place, use that ",
      "EXACT category name.\n",
      "2. NEVER invent a generic business-type category like \"regional_grocery\", ",
      "\"casual_dining\", \"fast_casual\", \"grocery_store\", or \"local_restaurant\" - these hide ",
      "the actual place and are USELESS for a foodborne illness traceback, which requires ",
      "knowing exactly which specific establishment was involved.\n",
      "3. If the item names any identifiable specific business, chain, or restaurant (even a ",
      "small independent one you don't otherwise know), use a lowercase_snake_case version of ",
      "THAT EXACT NAME as the category (e.g. \"harris_teeter\", \"joes_pizza_downtown\"). Do not ",
      "abstract it into a category of business.\n",
      "4. ONLY if the respondent's answer truly contains NO identifiable name at all (e.g. they ",
      "wrote just \"a restaurant\" or \"the grocery store\" with zero distinguishing details) use ",
      "exactly \"unspecified_restaurant\" or \"unspecified_grocery_store\" - do not invent any ",
      "other generic bucket beyond these two exact fallback labels.\n"
    )
  }

  prompt <- paste0(
    "You are maintaining a GROWING category taxonomy for a citizen-science foodborne ",
    "illness investigation. Respondents write vague, hedged, or typo'd free text.\n\n",
    "Categories that ALREADY EXIST: ", paste(known_categories, collapse = ", "), "\n\n",
    "For each item below:\n",
    domain_instructions, "\n",
    "Respond with ONLY a raw JSON object mapping each exact input item (as written, as the ",
    "key) to its category (as the value). No prose, no markdown code fences.\n\nItems:\n",
    # Items are already punctuation-normalised by split_freetext(), but
    # normalise again here so this function is safe to call directly: these
    # strings become JSON keys that Claude must echo back verbatim, and a
    # curly apostrophe on either side breaks the exact-name lookup.
    paste0("- ", normalize_punct(items), collapse = "\n")
  )
  resp <- tryCatch({
    httr2::request("https://api.anthropic.com/v1/messages") %>%
      httr2::req_headers("x-api-key" = api_key, "anthropic-version" = "2023-06-01",
                          "content-type" = "application/json") %>%
      httr2::req_body_json(list(model = model, max_tokens = 4096,
                                 messages = list(list(role = "user", content = prompt)))) %>%
      httr2::req_perform()
  }, error = function(e) NULL)
  if (is.null(resp)) return(NULL)
  text_out <- str_remove_all(httr2::resp_body_json(resp)$content[[1]]$text, "```json|```")
  tryCatch(jsonlite::fromJSON(text_out), error = function(e) NULL)
}

classify_items_dynamic <- function(items, known_categories, dict, domain = c("produce", "store"), method = c("llm", "regex")) {
  domain <- match.arg(domain)
  method <- match.arg(method)
  if (length(items) == 0) return(list(mapping = character(0), vocab = known_categories))
  if (method == "regex") {
    mapping <- setNames(map_chr(items, ~ regex_classify(.x, dict)), items)
    return(list(mapping = mapping, vocab = merge_categories(known_categories, mapping)))
  }
  result <- call_claude_classify_dynamic(items, known_categories, domain = domain)
  if (is.null(result) || length(result) == 0) {
    mapping <- setNames(map_chr(items, ~ regex_classify(.x, dict)), items)
    return(list(mapping = mapping, vocab = merge_categories(known_categories, mapping)))
  }
  mapping <- unlist(result)[items]
  mapping <- str_replace_all(str_to_lower(str_trim(mapping)), "[^a-z0-9]+", "_")
  mapping <- str_replace_all(mapping, "^_|_$", "")
  names(mapping) <- items
  missing <- is.na(mapping) | mapping == ""
  if (any(missing)) mapping[missing] <- map_chr(items[missing], ~ regex_classify(.x, dict))
  list(mapping = mapping, vocab = merge_categories(known_categories, mapping))
}

## Classifies free text AND grows the vocabulary in one step - CACHE-FIRST:
## any raw phrase already decided in a previous run gets its locked-in
## answer from item_map, no LLM call, no chance of drifting to a
## different answer. Only phrases genuinely never seen before go to the
## LLM, and that one-time decision gets saved into item_map permanently.
classify_and_grow <- function(raw_text_vec, known_categories, item_map, dict, domain = "produce", method = "llm") {
  long <- split_freetext(raw_text_vec)
  if (nrow(long) == 0) return(list(long = long %>% mutate(category = character(0)), vocab = known_categories, item_map = item_map))

  distinct_items <- unique(long$item)

  cached_category <- vapply(distinct_items, function(it) {
    val <- item_map[[it]]
    if (is.null(val)) NA_character_ else as.character(val)
  }, character(1))
  names(cached_category) <- distinct_items

  uncached_items <- distinct_items[is.na(cached_category)]

  if (length(uncached_items) > 0) {
    result <- classify_items_dynamic(uncached_items, known_categories, dict, domain = domain, method = method)
    known_categories <- result$vocab
    cached_category[uncached_items] <- result$mapping[uncached_items]
    # Only cache real decisions. An NA means we couldn't classify the
    # phrase this run (usually a failed/unparseable API call), and
    # writing that to item_map would lock the failure in permanently -
    # the cache is checked before the LLM, so it would never be retried.
    for (it in uncached_items) {
      decided <- unname(cached_category[[it]])
      if (!is.na(decided)) item_map[[it]] <- decided
    }
  }

  list(
    # Undecided items drop out of this run's counts entirely rather than
    # forming an NA category row in the frequency tables. The response
    # still counts toward n_total; it just contributes no exposure.
    long = long %>%
      mutate(category = unname(cached_category[item])) %>%
      filter(!is.na(category)),
    vocab = known_categories,
    item_map = item_map
  )
}
```

```{r load-data}
raw <- read_sheet(SHEET_URL)
present_map <- match_columns(names(raw), col_signatures)

df <- raw %>%
  select(all_of(unname(present_map))) %>%
  rename(!!!present_map) %>%
  clean_names() %>%
  mutate(response_id = row_number())

if ("consent" %in% names(df)) {
  df <- df %>%
    filter(str_detect(str_to_lower(str_trim(as.character(consent))), "^yes"))
}

n_total <- nrow(df)

duration_summary <- if ("duration" %in% names(df)) {
  df %>%
    count(duration, sort = TRUE, name = "n_responses") %>%
    mutate(pct = round(100 * n_responses / n_total, 1))
} else tibble()

vocab <- load_vocabulary(VOCAB_PATH, names(produce_dict_seed), names(store_dict_seed), baseline_commonness_seed)

## The two produce columns are NO LONGER concatenated. They are different
## kinds of data and get different treatment: checklist answers are preset
## strings resolved by direct lookup, free text goes to the classifier.
## Concatenating them meant ~90% of the volume was being sent through an LLM
## that had nothing to decide, which is both wasted spend and a source of
## drift the checklist can't actually suffer from.
produce_checklist_raw <- if ("produce_checklist" %in% names(df)) as.character(df$produce_checklist) else NULL
produce_freetext_raw  <- if ("produce_other" %in% names(df)) as.character(df$produce_other) else NULL

## CHECKLIST PATH - direct lookup, no LLM, no regex, no cache writes.
produce_checklist_long <- if (!is.null(produce_checklist_raw)) {
  classify_checklist(produce_checklist_raw) %>%
    mutate(response_id = row_id, source_type = "checklist_direct", .keep = "unused")
} else tibble()

## FREE-TEXT PATH - unchanged: classify, grow the vocabulary, cache.
produce_freetext_long <- if (!is.null(produce_freetext_raw)) {
  r <- classify_and_grow(produce_freetext_raw, vocab$produce_categories, vocab$produce_item_map,
                         produce_dict_seed, domain = "produce", method = CLASSIFICATION_METHOD)
  vocab$produce_categories <- r$vocab
  vocab$produce_item_map   <- r$item_map
  r$long %>% mutate(response_id = row_id, source_type = "freetext_classified", .keep = "unused")
} else tibble()

produce_long <- bind_rows(produce_checklist_long, produce_freetext_long)

## Every category the checklist can produce must exist in the vocabulary,
## including any legacy bucket the map routes to (lettuce_unspecified).
vocab$produce_categories <- union(vocab$produce_categories,
                                  unique(unlist(unname(checklist_map))))

## Label any category that arrived without provenance - newly minted by the
## classifier, pulled in by the checklist union, or added by hand. Runs after
## every route that can add one, and never overwrites an existing label.
vocab <- stamp_category_provenance(vocab, unique(unlist(unname(checklist_map))))

if ("shop_raw" %in% names(df)) {
  store_result <- classify_and_grow(df$shop_raw, vocab$store_categories, vocab$store_item_map, store_dict_seed, domain = "store", method = CLASSIFICATION_METHOD)
  store_long <- store_result$long %>% mutate(response_id = row_id, .keep = "unused")
  vocab$store_categories <- store_result$vocab
  vocab$store_item_map <- store_result$item_map
} else {
  store_long <- tibble()
}

# NOTE: the vocabulary is NOT persisted here. It is written in the final
# chunk of this document, once every chart and table has rendered - so an
# interrupted render can't leave a saved vocabulary with no corresponding
# page. See "persist-vocabulary" at the end of the file.

# 95% Wilson score CI on each proportion - stays sane at small n and near
# 0%/100%, unlike the naive normal approximation. Base R only.
wilson_ci <- function(x, n, conf_level = 0.95) {
  if (n == 0) return(c(lower = NA_real_, upper = NA_real_))
  p_hat <- x / n
  z <- qnorm(1 - (1 - conf_level) / 2)
  denom <- 1 + z^2 / n
  center <- p_hat + z^2 / (2 * n)
  adj <- z * sqrt((p_hat * (1 - p_hat) + z^2 / (4 * n)) / n)
  c(lower = max(0, (center - adj) / denom), upper = min(1, (center + adj) / denom))
}

add_wilson_ci <- function(freq_df, n_total) {
  ci <- purrr::map2_dfr(freq_df$n_cases, n_total, ~ as.list(wilson_ci(.x, .y)))
  freq_df %>%
    mutate(ci_low_pct = round(ci$lower * 100, 1), ci_high_pct = round(ci$upper * 100, 1))
}

produce_freq <- produce_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

store_freq <- store_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

## External reference baselines from USDA ERS, for DISPLAY ONLY. These are
## never fed into signal_ratio: ERS publishes pounds of per-capita
## availability per year, while baseline_commonness is a 0-100 "percent of
## people who ate this in a two-week period" scale. The two are not
## convertible, so showing both side by side is honest and substituting one
## for the other would not be. Reconciling the units is future work.
EXTERNAL_BASELINES_PATH <- "baselines-external.json"

external_baselines <- if (file.exists(EXTERNAL_BASELINES_PATH)) {
  eb <- tryCatch(jsonlite::fromJSON(EXTERNAL_BASELINES_PATH, simplifyVector = FALSE),
                 error = function(e) NULL)
  if (is.null(eb$baselines)) list() else eb$baselines
} else list()

ers_reference <- function(cat) {
  e <- external_baselines[[cat]]
  if (is.null(e) || is.null(e$value_lb_per_year)) return(NA_character_)
  sprintf("%.1f lb/yr (%s)", e$value_lb_per_year, e$source_year)
}

produce_signal <- produce_freq %>%
  mutate(baseline_pct = unlist(vocab$baseline_commonness)[category]) %>%
  filter(!is.na(baseline_pct)) %>%
  mutate(
    signal_ratio = round(pct_of_cases / baseline_pct, 2),
    signal_ratio_low = round(ci_low_pct / baseline_pct, 2),
    signal_ratio_high = round(ci_high_pct / baseline_pct, 2),
    baseline_confidence = vapply(category, function(c) {
      v <- vocab$baseline_confidence[[c]]; if (is.null(v)) "unsourced" else as.character(v)
    }, character(1)),
    ers_ref = vapply(category, ers_reference, character(1)),
    ## BASELINE SENSITIVITY BAND, author-estimated baselines only.
    ## A flat +/-30% on the baseline, propagated through the ratio: because
    ## the baseline is the DENOMINATOR, a larger baseline gives a smaller
    ## ratio, hence the inversion below. Deliberately one flat width for
    ## every estimate rather than a hand-tuned width per category - a
    ## per-category width would imply we know which guesses are shakier
    ## than others, and we don't yet. Refining that is a future improvement,
    ## not a judgement being made here. ERS-sourced baselines get no band.
    baseline_sens_low  = ifelse(baseline_confidence == "unsourced",
                                round(pct_of_cases / (baseline_pct * 1.3), 2), NA_real_),
    baseline_sens_high = ifelse(baseline_confidence == "unsourced",
                                round(pct_of_cases / (baseline_pct * 0.7), 2), NA_real_)
  ) %>%
  # Sort by conservative lower-bound ratio, not the raw point estimate -
  # discounts small-n flukes, rewards foods elevated even pessimistically.
  arrange(desc(signal_ratio_low), desc(signal_ratio))

n_ers_sourced <- sum(produce_signal$baseline_confidence == "exact_match")
n_estimated   <- sum(produce_signal$baseline_confidence == "unsourced")
```

```{r derived-data}
## Everything below precomputes data used by BOTH a chart (shown early on
## the page) and its companion table (shown in the Data Tables section at
## the bottom) - centralizing this here means the chart and its table can
## never disagree, and moving chunks around the page later won't break
## anything since both draw from these same precomputed objects.

# --- US state counts ---
normalize_state <- function(x) {
  x <- str_trim(x)
  full_match <- state.name[match(str_to_title(x), state.name)]
  abbr_match <- state.name[match(str_to_upper(x), state.abb)]
  dc_match <- ifelse(
    str_to_lower(x) %in% c("dc", "washington dc", "washington, dc", "district of columbia"),
    "District of Columbia", NA_character_
  )
  coalesce(full_match, abbr_match, dc_match)
}

state_counts <- if ("state" %in% names(df)) {
  df %>%
    mutate(state = normalize_state(state)) %>%
    filter(!is.na(state)) %>%
    count(state, name = "n_cases") %>%
    arrange(desc(n_cases))
} else {
  tibble()
}

# --- Canadian province counts ---
canada_provinces <- c("British Columbia", "Alberta", "Saskatchewan", "Manitoba", "Ontario",
                       "Quebec", "New Brunswick", "Nova Scotia", "Prince Edward Island",
                       "Newfoundland and Labrador")

mapcan_available <- requireNamespace("mapcan", quietly = TRUE)

province_counts <- if ("state" %in% names(df)) {
  df %>%
    mutate(province = str_trim(state)) %>%
    filter(province %in% canada_provinces) %>%
    count(province, name = "n_cases") %>%
    arrange(desc(n_cases))
} else {
  tibble()
}

# --- Epi curve data ---
epi_curve_data <- if ("onset_date" %in% names(df)) {
  df %>%
    mutate(onset_date = suppressWarnings(
      lubridate::parse_date_time(onset_date,
        orders = c("mdy", "ymd", "dmy", "mdY HMS", "ymd HMS"))
    )) %>%
    mutate(onset_date = as_date(onset_date)) %>%
    filter(!is.na(onset_date)) %>%
    count(onset_date, name = "cases") %>%
    arrange(onset_date)
} else {
  tibble()
}

# --- Reddit tally data (separate spreadsheet from the main form) ---
RESTAURANT_UR = "https://docs.google.com/spreadsheets/d/1t-IXTcBjtrI7bP9HFRPlVluc3oVNWjnjYLTPg6DrlXE/edit?usp=sharing"
tally_data <- tryCatch(
  read_sheet(RESTAURANT_UR, sheet = "Restaurant_Food_Tally"),
  error = function(e) NULL
)

if (!is.null(tally_data) && nrow(tally_data) > 0) {
  names(tally_data)[1:3] <- c("restaurant", "food", "mentions")
  tally_data <- tally_data %>% filter(!is.na(restaurant), !is.na(food))
} else {
  tally_data <- tibble(restaurant = character(), food = character(), mentions = numeric())
}

top_tally_foods <- tally_data %>%
  group_by(food) %>%
  summarise(total = sum(mentions, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(total)) %>%
  slice_head(n = 15) %>%
  pull(food)

tally_plot_data <- tally_data %>%
  filter(food %in% top_tally_foods) %>%
  mutate(food = factor(food, levels = top_tally_foods))
```

# Crowdsourced Cyclospora Watch

*Last updated: `r format(Sys.time(), "%B %d, %Y at %I:%M %p %Z")`*

# Feeling sick or have a confirmed case of cyclospora? [Submit your report here](https://forms.gle/QxB54kJSZV4cCFzQ6)

**`r n_total`** responses collected so far. This is a self-reported, crowdsourced
tracker built to try to spot patterns
in the current multistate cyclospora outbreak — **not** an official CDC or
state health department investigation. There is no control group, so results
below are proportional reporting among people who got sick, not proof of cause.
Treat this as "worth watching," not "confirmed."

---

# Charts

## Chart 1: Top Produce Leads by Signal Ratio

Sorted by signal ratio — how much more often cases report eating this
compared to how often people eat it in an ordinary two-week period. A ratio
above 1 means it's showing up more than you'd expect from typical diets.

```{r produce-signal-plot, fig.width=9, fig.height=6}
## Two DIFFERENT uncertainties are drawn here and they must stay visually
## distinct:
##   - dark whiskers  = 95% Wilson CI on the case proportion (sampling error)
##   - pale wide band = +/-30% on an author-estimated baseline (input error)
## A category with a sourced ERS baseline gets no pale band, which is the
## point: it makes "we guessed this denominator" visible at a glance.
produce_signal %>%
  filter(n_cases >= 3) %>%
  ggplot(aes(x = reorder(category, signal_ratio_low), y = signal_ratio)) +
  geom_linerange(aes(ymin = baseline_sens_low, ymax = baseline_sens_high),
                 linewidth = 6, colour = "#f0c9a8", na.rm = TRUE) +
  geom_col(aes(fill = signal_ratio), width = 0.62) +
  scale_fill_viridis_c(option = "inferno", guide = "none") +
  geom_errorbar(aes(ymin = signal_ratio_low, ymax = signal_ratio_high),
                width = 0.3, color = "gray30") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  coord_flip() +
  labs(title = "Produce Signal Ratio",
       subtitle = paste0("Bars = point estimate  |  dark whiskers = 95% CI on the case %  |  ",
                         "pale band = ±30% uncertainty on an estimated baseline"),
       x = NULL, y = "Signal ratio (case % / baseline %)") +
  theme_minimal(base_size = 13)
```

*See Table 1 below for the full data, including confidence intervals.*

## Chart 2: Cases by State

```{r state-map, fig.width=9, fig.height=6}
if (nrow(state_counts) > 0) {
  # Using the base "maps" package instead of usmap/sf - pure data, no
  # compiled system libraries required, so this can't break the same
  # way again. Trade-off: contiguous 48 states only (no AK/HI/DC as
  # separate shapes) - acceptable for this use case.
  us_states <- map_data("state")
  map_df <- us_states %>%
    left_join(state_counts %>% mutate(region = str_to_lower(state)), by = "region")

  ggplot(map_df, aes(long, lat, group = group, fill = n_cases)) +
    geom_polygon(color = "white", linewidth = 0.2) +
    scale_fill_viridis_c(option = "inferno", direction = -1, name = "Self-reported cases", na.value = "gray90") +
    coord_fixed(1.3) +
    theme_void() +
    labs(title = "Self-Reported Cases by State (contiguous 48 states)")
} else {
  cat("*No state data could be matched yet.*")
}
```

*This is a representation of the cases that have been self-reported in
this survey. For the official case count, please refer to the CDC or
your relevant state/local health department. See Table 2 below for the
full state-by-state count.*

## Chart 3: Cases by Canadian Province

```{r canada-map, fig.width=9, fig.height=7}
if (mapcan_available && nrow(province_counts) > 0) {
  province_shapes <- mapcan::mapcan(boundaries = province, type = standard)

  province_map_data <- province_shapes %>%
    left_join(province_counts, by = c("pr_english" = "province"))

  ggplot(province_map_data, aes(long, lat, group = group, fill = n_cases)) +
    geom_polygon(color = "white") +
    scale_fill_viridis_c(option = "inferno", direction = -1, name = "Self-reported cases", na.value = "gray90") +
    coord_fixed() +
    theme_void() +
    labs(title = "Self-Reported Cases by Province")
} else if (!mapcan_available) {
  cat("*Province map unavailable this run (mapcan package not installed).*")
} else {
  cat("*No Canadian responses yet.*")
}
```

*See Table 3 below for the full province-by-province count.*

## Chart 4: Epi Curve

```{r epi-curve, fig.width=10, fig.height=5}
if (nrow(epi_curve_data) > 0) {
  ggplot(epi_curve_data, aes(onset_date, cases)) +
    geom_col(aes(fill = cases)) +
    scale_fill_viridis_c(option = "inferno", guide = "none") +
    scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
    labs(title = "Epi Curve: Self-Reported Symptom Onset Dates",
         x = "Onset date", y = "Cases") +
    theme_minimal(base_size = 13) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("*No onset date data available yet.*")
}
```

*See Table 4 below for the full date-by-date case counts.*

## Chart 5: Reddit Thread Parsed Sources

This is a hand-compiled tally of food/restaurant mentions from Reddit threads,
kept separate from the statistical analysis above since it doesn't have the
per-person structure needed for the confidence intervals or signal ratios.
Read as "what's been mentioned together," not as a statistical finding.

```{r restaurant-food-tally, fig.width=11, fig.height=6}
if (nrow(tally_plot_data) > 0) {
  ggplot(tally_plot_data, aes(x = food, y = mentions, fill = restaurant)) +
    geom_col(position = position_dodge(preserve = "single"), color = "white", linewidth = 0.2) +
    scale_fill_viridis_d(option = "inferno") +
    theme_minimal(base_size = 12) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Reddit Mentions: Top 15 Foods by Restaurant/Source",
         x = NULL, y = "Mentions", fill = "Restaurant/Source")
} else {
  cat("*No tally data found yet - add a 'Restaurant_Food_Tally' tab to the sheet.*")
}
```

*See Table 5 below for the full mention tally (all restaurants/foods, not
just the top 15 shown here).*

---

# Data Tables

## Table 1: Produce Signal Ratio (Full Data)

```{r produce-signal-table}
## Column order here must match produce_signal's, so build the display frame
## explicitly rather than relying on however mutate() happened to order it.
produce_signal %>%
  transmute(
    category, n_cases, pct_of_cases, ci_low_pct, ci_high_pct,
    baseline_pct,
    baseline_confidence = ifelse(baseline_confidence == "exact_match",
                                 "USDA ERS", "author estimate"),
    ers_ref = ifelse(is.na(ers_ref), "—", ers_ref),
    signal_ratio, signal_ratio_low, signal_ratio_high
  ) %>%
  datatable(
    rownames = FALSE,
    colnames = c("Food", "# cases", "% of cases", "CI low", "CI high",
                 "Baseline % (used in ratio)", "Baseline source",
                 "ERS reference (not used in ratio)",
                 "Signal ratio", "Ratio CI low", "Ratio CI high"),
    options = list(pageLength = 10, order = list(list(8, "desc")), scrollX = TRUE))
```

*CI columns are a 95% confidence interval — small sample sizes mean wide
ranges. If the "Ratio CI low" column is still above 1, that's a stronger
lead than the point estimate alone.*

### Where these baselines come from

The signal ratio divides how often cases report a food by a **baseline** —
how commonly people eat it normally. That denominator drives every number
in this table, so it's worth being explicit about where it comes from.

```{r baseline-provenance-note, results="asis"}
cat(sprintf(
"Of the %d foods below, **%d have a baseline sourced from USDA ERS** and
**%d rest on the author's own estimate**. Both are labeled in the
\"Baseline source\" column.\n\n", n_ers_sourced + n_estimated, n_ers_sourced, n_estimated))
```

- **Author estimates** are exactly that — considered guesses, not
  measurements, and not derived from any survey. They carry a **pale ±30%
  band** on the chart above to show roughly how much the ratio would move if
  the guess were off by that much. The band is one flat width for every
  estimate; pretending to know which guesses are shakier than others would
  be false precision.
- **USDA ERS** values come from the
  [Food Availability (Per Capita) Data System](https://www.ers.usda.gov/data-products/food-availability-per-capita-data-system),
  refreshed monthly into `baselines-external.json`.

**The ERS column is shown but not yet used**, and the reason is a real
limitation rather than an oversight. ERS publishes *pounds of food available
per person per year*; the baseline this ratio needs is *the share of people
who ate a food in a two-week window*. Those measure different things and
cannot be converted into one another — 19 lb of tomatoes a year could be
everyone eating a little or a few people eating a lot. Substituting one for
the other would change every ratio on this page for no reason but a change
of units. Reconciling them properly is open work; until then both numbers
are shown side by side so the gap is visible rather than hidden.

Foods without any baseline at all don't appear in this table — they're still
counted in *All produce mentioned* further down.

## Table 2: Cases by State (Full Data)

```{r state-table}
if (nrow(state_counts) > 0) {
  datatable(state_counts, rownames = FALSE,
            colnames = c("State", "# cases"),
            options = list(pageLength = 10))
} else {
  cat("*No state data available yet.*")
}
```

## Table 3: Cases by Canadian Province (Full Data)

```{r province-table}
if (nrow(province_counts) > 0) {
  datatable(province_counts, rownames = FALSE,
            colnames = c("Province", "# cases"),
            options = list(pageLength = 10))
} else {
  cat("*No Canadian responses yet.*")
}
```

## Table 4: Epi Curve Data (Full Data)

```{r epi-curve-table}
if (nrow(epi_curve_data) > 0) {
  datatable(epi_curve_data, rownames = FALSE,
            colnames = c("Onset date", "Cases"),
            options = list(pageLength = 10))
} else {
  cat("*No onset date data available yet.*")
}
```

## Table 5: Reddit Mention Tally (Full Data)

```{r tally-table}
if (nrow(tally_data) > 0) {
  datatable(tally_data %>% arrange(desc(mentions)), rownames = FALSE,
            colnames = c("Restaurant/Source", "Food", "Mentions"),
            options = list(pageLength = 10))
} else {
  cat("*No tally data found yet - add a 'Restaurant_Food_Tally' tab to the sheet.*")
}
```

## Table 6: All Produce Mentioned

```{r produce-table}
datatable(produce_freq, rownames = FALSE,
          colnames = c("Food", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Table 7: Stores & Restaurants Mentioned

```{r store-table}
datatable(store_freq, rownames = FALSE,
          colnames = c("Store/restaurant", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Table 8: Reported Symptom Duration

Cyclospora illness tends to run longer than most foodborne bugs (often weeks,
sometimes relapsing). Short-duration reports are more likely something else.

```{r duration-table}
if (nrow(duration_summary) > 0) {
  datatable(duration_summary, rownames = FALSE,
            colnames = c("Duration", "# responses", "% of responses"),
            options = list(pageLength = 10))
}
```

---

**How to read this page:** a high signal ratio means the food is reported by
sick people more than you'd expect from normal eating habits — that's a lead
worth watching, not a verdict. Small numbers (a food only 2-3 people
mentioned) are noisy and easy to over-read. If something looks concerning and
consistent, the right next step is reporting it to your **local or state
health department**, who can do formal case-control interviews and trace
product lots — this page can't do that part.

*Want to add your own report? [Fill out the form here](https://forms.gle/6zFfhiaGcw7xHDKa7).*

```{r persist-vocabulary}
# Persist the (possibly grown) vocabulary so the next scheduled run reuses
# these categories instead of starting over. The GitHub Action commits this
# file alongside index.html.
#
# This runs LAST, deliberately. Every chart and table above has already
# rendered by now, so an interrupted or failed render can never leave a
# written vocabulary behind with no corresponding page. save_vocabulary()
# re-reads and merges before writing, so this is safe even if another run
# has touched the file while this one was rendering.
#
# Integrity is checked HERE rather than next to stamp_category_provenance(),
# because that runs before the store classification and so cannot see
# categories minted by it. This is the only point where every route that can
# add a category has finished.
vocab <- check_vocabulary_integrity(vocab)
save_vocabulary(vocab, VOCAB_PATH)
```
