---
title: "Crowdsourced Cyclospora Watch"
output:
  html_document:
    theme: flatly
    toc: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

required_pkgs <- c("googlesheets4", "dplyr", "tidyr", "stringr", "lubridate",
                    "ggplot2", "janitor", "purrr", "knitr", "DT", "httr2", "jsonlite", "maps")
new_pkgs <- required_pkgs[!(required_pkgs %in% installed.packages()[, "Package"])]
if (length(new_pkgs)) install.packages(new_pkgs)
library(googlesheets4); library(dplyr); library(tidyr); library(stringr)
library(lubridate); library(ggplot2); library(janitor); library(purrr)
library(knitr); library(DT)

## Shared pipeline core. These files are sourced by BOTH this report and
## cyclospora_outbreak_analysis.R, so a fix lands in one place instead of
## having to be applied twice and silently drifting when it isn't. What stays
## in this file is config (the sheet, the seeds, the column signatures) and
## presentation - the report's own tables, charts and prose.
source("R/columns.R")               # match_columns
source("R/text-normalize.R")       # normalize_punct, split_delims, is_negation, split_freetext
source("R/vocabulary-io.R")        # read/load/save vocabulary, stamp_category_provenance
source("R/checklist.R")            # checklist_map + classify_checklist
source("R/classify.R")             # regex + LLM classification, classify_and_grow
source("R/stats.R")                 # wilson_ci, add_wilson_ci
source("R/run-manifest.R")          # build/write run-manifest.json
source("R/vocabulary-integrity.R") # assert_utf8_locale, check_vocabulary_integrity

## Runs before any text is read: under a non-UTF-8 locale normalize_punct()
## silently does nothing, and every curly apostrophe forks a duplicate category.
assert_utf8_locale()
```

```{r config}
# ---- EDIT THIS SECTION FOR YOUR FORM ----
SHEET_URL <- "https://docs.google.com/spreadsheets/d/1n1VJ99Ko7mvFQmKRX_QrFLFFziMAGKpkUNmK40QxLpU/edit?usp=sharing"
gs4_deauth()

col_signatures <- c(
  timestamp        = "^timestamp$",
  consent          = "consent",
  state            = "what state",
  why_believe      = "why do you believe",
  produce_checklist = "did you eat any of the following",
  produce_other    = "anything else you remember eating",
  shop_raw         = "shop.?dine",
  duration         = "how long did symptoms last",
  onset_date       = "when did symptoms start"
)

## Without `consent` the filter that drops non-consenting responses is skipped
## silently, so it is required rather than optional. Either produce column will
## do, but with neither there is no exposure data to analyse.
REQUIRED_COLUMNS    <- c("consent")
REQUIRE_ANY_COLUMNS <- list(c("produce_checklist", "produce_other"))

# Seed dictionaries - starting point + offline fallback only. The real,
# growing vocabulary lives in category_vocabulary.json (see below).
produce_dict_seed <- list(
  # Lettuce is split into whole-head vs prepackaged/bagged - this
  # distinction matters a lot for traceback (prepackaged/bagged salad is
  # the recurring outbreak vehicle, whole heads much less so), so we keep
  # them as separate categories rather than merging into one "lettuce".
  romaine_head        = "romaine.*head|head.*romaine|whole romaine",
  romaine_prepackaged = "romaine.*(prepackag|bagged)|bagged romaine",
  iceberg_head        = "iceberg.*head|head.*iceberg|whole iceberg",
  iceberg_prepackaged = "iceberg.*(prepackag|bagged)|bagged iceberg",
  mesclun_spring_mix  = "mesclun|spring mix",
  spinach = "spinach", cilantro = "cilantro|coriander", basil = "\\bbasil\\b",
  parsley = "parsley", raspberries = "raspberr", strawberries = "strawberr",
  blackberries = "blackberr", cucumber = "cucumber", tomato = "tomato",
  snap_peas = "snap pea|sugar snap", green_onion = "green onion|scallion|spring onion",
  cabbage = "cabbage|slaw", carrot = "carrot", broccoli = "broccoli",
  melon = "cantaloupe|honeydew|melon", bell_pepper = "bell pepper|sweet pepper",
  avocado = "avocado|guacamole", celery = "celery", cauliflower = "cauliflower",
  dill = "\\bdill\\b", radish = "radish",
  mint = "\\bmint\\b",
  # Generic bagged/premade salad where the specific lettuce type isn't
  # named - catches free-text synonyms like "premade salad", "pre-made
  # side salad", "grab and go salad" so they land here instead of
  # spawning a near-duplicate category.
  salad_bagged = "bagged salad|salad kit|salad mix|premade salad|pre-made salad|pre made salad|ready.to.eat salad|grab.and.go salad",
  salad_restaurant = "restaurant salad|salad bar"
)

store_dict_seed <- list(
  kroger = "kroger", trader_joes = "trader joe", whole_foods = "whole foods",
  walmart = "wal[- ]?mart", target = "\\btarget\\b", publix = "publix",
  aldi = "aldi", costco = "costco", safeway = "safeway", wegmans = "wegmans",
  taco_bell = "taco bell", chipotle = "chipotle", subway = "subway",
  mcdonalds = "mcdonald", local_farmers_market = "farmers?[- ]?market",
  local_restaurant = "^restaurant$|local restaurant"
)

baseline_commonness_seed <- c(
  # Old single "lettuce" baseline (55) split across the new granular
  # categories - rough guesses, tune as you like.
  romaine_head = 15, romaine_prepackaged = 20, iceberg_head = 10,
  iceberg_prepackaged = 12, mesclun_spring_mix = 8,
  spinach = 25, cilantro = 20, basil = 10, parsley = 12,
  raspberries = 10, strawberries = 30, blackberries = 8, cucumber = 30,
  tomato = 45, snap_peas = 8, green_onion = 20, cabbage = 15, carrot = 40,
  broccoli = 35, melon = 20, bell_pepper = 30, avocado = 35, celery = 15,
  cauliflower = 15, dill = 8,
  radish = 6, mint = 5, salad_bagged = 25, salad_restaurant = 20
)

VOCAB_PATH <- "category_vocabulary.json"

```

```{r functions}
# The pipeline functions that used to live here are now in R/, sourced in the
# setup chunk above. What remains is the one knob a maintainer actually edits.
CLASSIFICATION_METHOD <- "llm"   # "llm" or "regex"
```

```{r load-data}
raw <- read_sheet(SHEET_URL)
present_map <- match_columns(names(raw), col_signatures,
                              required = REQUIRED_COLUMNS,
                              require_any = REQUIRE_ANY_COLUMNS)

df <- raw %>%
  select(all_of(unname(present_map))) %>%
  rename(!!!present_map) %>%
  clean_names() %>%
  mutate(response_id = row_number())

if ("consent" %in% names(df)) {
  df <- df %>%
    filter(str_detect(str_to_lower(str_trim(as.character(consent))), "^yes"))
}

n_total <- nrow(df)

duration_summary <- if ("duration" %in% names(df)) {
  df %>%
    count(duration, sort = TRUE, name = "n_responses") %>%
    mutate(pct = round(100 * n_responses / n_total, 1))
} else tibble()

vocab <- load_vocabulary(VOCAB_PATH, names(produce_dict_seed), names(store_dict_seed), baseline_commonness_seed)

## The two produce columns are NO LONGER concatenated. They are different
## kinds of data and get different treatment: checklist answers are preset
## strings resolved by direct lookup, free text goes to the classifier.
## Concatenating them meant ~90% of the volume was being sent through an LLM
## that had nothing to decide, which is both wasted spend and a source of
## drift the checklist can't actually suffer from.
produce_checklist_raw <- if ("produce_checklist" %in% names(df)) as.character(df$produce_checklist) else NULL
produce_freetext_raw  <- if ("produce_other" %in% names(df)) as.character(df$produce_other) else NULL

## CHECKLIST PATH - direct lookup, no LLM, no regex, no cache writes.
produce_checklist_long <- if (!is.null(produce_checklist_raw)) {
  classify_checklist(produce_checklist_raw) %>%
    mutate(response_id = row_id, source_type = "checklist_direct", .keep = "unused")
} else tibble()

## FREE-TEXT PATH - unchanged: classify, grow the vocabulary, cache.
produce_freetext_long <- if (!is.null(produce_freetext_raw)) {
  r <- classify_and_grow(produce_freetext_raw, vocab$produce_categories, vocab$produce_item_map,
                         produce_dict_seed, domain = "produce", method = CLASSIFICATION_METHOD)
  vocab$produce_categories <- r$vocab
  vocab$produce_item_map   <- r$item_map
  r$long %>% mutate(response_id = row_id, source_type = "freetext_classified", .keep = "unused")
} else tibble()

produce_long <- bind_rows(produce_checklist_long, produce_freetext_long)

## Every category the checklist can produce must exist in the vocabulary,
## including any legacy bucket the map routes to (lettuce_unspecified).
vocab$produce_categories <- union(vocab$produce_categories,
                                  unique(unlist(unname(checklist_map))))

## Label any category that arrived without provenance - newly minted by the
## classifier, pulled in by the checklist union, or added by hand. Runs after
## every route that can add one, and never overwrites an existing label.
vocab <- stamp_category_provenance(vocab, unique(unlist(unname(checklist_map))))

if ("shop_raw" %in% names(df)) {
  store_result <- classify_and_grow(df$shop_raw, vocab$store_categories, vocab$store_item_map, store_dict_seed, domain = "store", method = CLASSIFICATION_METHOD)
  store_long <- store_result$long %>% mutate(response_id = row_id, .keep = "unused")
  vocab$store_categories <- store_result$vocab
  vocab$store_item_map <- store_result$item_map
} else {
  store_long <- tibble()
}

# NOTE: the vocabulary is NOT persisted here. It is written in the final
# chunk of this document, once every chart and table has rendered - so an
# interrupted render can't leave a saved vocabulary with no corresponding
# page. See "persist-vocabulary" at the end of the file.


produce_freq <- produce_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

store_freq <- store_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

## External reference baselines from USDA ERS, for DISPLAY ONLY. These are
## never fed into signal_ratio: ERS publishes pounds of per-capita
## availability per year, while baseline_commonness is a 0-100 "percent of
## people who ate this in a two-week period" scale. The two are not
## convertible, so showing both side by side is honest and substituting one
## for the other would not be. Reconciling the units is future work.
EXTERNAL_BASELINES_PATH <- "baselines-external.json"

external_baselines <- if (file.exists(EXTERNAL_BASELINES_PATH)) {
  eb <- tryCatch(jsonlite::fromJSON(EXTERNAL_BASELINES_PATH, simplifyVector = FALSE),
                 error = function(e) NULL)
  if (is.null(eb$baselines)) list() else eb$baselines
} else list()

ers_reference <- function(cat) {
  e <- external_baselines[[cat]]
  if (is.null(e) || is.null(e$value_lb_per_year)) return(NA_character_)
  sprintf("%.1f lb/yr (%s)", e$value_lb_per_year, e$source_year)
}

produce_signal <- produce_freq %>%
  mutate(baseline_pct = unlist(vocab$baseline_commonness)[category]) %>%
  filter(!is.na(baseline_pct)) %>%
  mutate(
    signal_ratio = round(pct_of_cases / baseline_pct, 2),
    signal_ratio_low = round(ci_low_pct / baseline_pct, 2),
    signal_ratio_high = round(ci_high_pct / baseline_pct, 2),
    baseline_confidence = vapply(category, function(c) {
      v <- vocab$baseline_confidence[[c]]; if (is.null(v)) "unsourced" else as.character(v)
    }, character(1)),
    ers_ref = vapply(category, ers_reference, character(1)),
    ## BASELINE SENSITIVITY BAND, author-estimated baselines only.
    ## A flat +/-30% on the baseline, propagated through the ratio: because
    ## the baseline is the DENOMINATOR, a larger baseline gives a smaller
    ## ratio, hence the inversion below. Deliberately one flat width for
    ## every estimate rather than a hand-tuned width per category - a
    ## per-category width would imply we know which guesses are shakier
    ## than others, and we don't yet. Refining that is a future improvement,
    ## not a judgement being made here. ERS-sourced baselines get no band.
    baseline_sens_low  = ifelse(baseline_confidence == "unsourced",
                                round(pct_of_cases / (baseline_pct * 1.3), 2), NA_real_),
    baseline_sens_high = ifelse(baseline_confidence == "unsourced",
                                round(pct_of_cases / (baseline_pct * 0.7), 2), NA_real_)
  ) %>%
  # Sort by conservative lower-bound ratio, not the raw point estimate -
  # discounts small-n flukes, rewards foods elevated even pessimistically.
  arrange(desc(signal_ratio_low), desc(signal_ratio))

n_ers_sourced <- sum(produce_signal$baseline_confidence == "exact_match")
n_estimated   <- sum(produce_signal$baseline_confidence == "unsourced")
```

```{r derived-data}
## Everything below precomputes data used by BOTH a chart (shown early on
## the page) and its companion table (shown in the Data Tables section at
## the bottom) - centralizing this here means the chart and its table can
## never disagree, and moving chunks around the page later won't break
## anything since both draw from these same precomputed objects.

# --- US state counts ---
normalize_state <- function(x) {
  x <- str_trim(x)
  full_match <- state.name[match(str_to_title(x), state.name)]
  abbr_match <- state.name[match(str_to_upper(x), state.abb)]
  dc_match <- ifelse(
    str_to_lower(x) %in% c("dc", "washington dc", "washington, dc", "district of columbia"),
    "District of Columbia", NA_character_
  )
  coalesce(full_match, abbr_match, dc_match)
}

state_counts <- if ("state" %in% names(df)) {
  df %>%
    mutate(state = normalize_state(state)) %>%
    filter(!is.na(state)) %>%
    count(state, name = "n_cases") %>%
    arrange(desc(n_cases))
} else {
  tibble()
}

# --- Canadian province counts ---
canada_provinces <- c("British Columbia", "Alberta", "Saskatchewan", "Manitoba", "Ontario",
                       "Quebec", "New Brunswick", "Nova Scotia", "Prince Edward Island",
                       "Newfoundland and Labrador")

mapcan_available <- requireNamespace("mapcan", quietly = TRUE)

province_counts <- if ("state" %in% names(df)) {
  df %>%
    mutate(province = str_trim(state)) %>%
    filter(province %in% canada_provinces) %>%
    count(province, name = "n_cases") %>%
    arrange(desc(n_cases))
} else {
  tibble()
}

# --- Epi curve data ---
epi_curve_data <- if ("onset_date" %in% names(df)) {
  df %>%
    mutate(onset_date = suppressWarnings(
      lubridate::parse_date_time(onset_date,
        orders = c("mdy", "ymd", "dmy", "mdY HMS", "ymd HMS"))
    )) %>%
    mutate(onset_date = as_date(onset_date)) %>%
    filter(!is.na(onset_date)) %>%
    count(onset_date, name = "cases") %>%
    arrange(onset_date)
} else {
  tibble()
}

# --- Reddit tally data (separate spreadsheet from the main form) ---
RESTAURANT_UR = "https://docs.google.com/spreadsheets/d/1t-IXTcBjtrI7bP9HFRPlVluc3oVNWjnjYLTPg6DrlXE/edit?usp=sharing"
tally_data <- tryCatch(
  read_sheet(RESTAURANT_UR, sheet = "Restaurant_Food_Tally"),
  error = function(e) NULL
)

if (!is.null(tally_data) && nrow(tally_data) > 0) {
  names(tally_data)[1:3] <- c("restaurant", "food", "mentions")
  tally_data <- tally_data %>% filter(!is.na(restaurant), !is.na(food))
} else {
  tally_data <- tibble(restaurant = character(), food = character(), mentions = numeric())
}

top_tally_foods <- tally_data %>%
  group_by(food) %>%
  summarise(total = sum(mentions, na.rm = TRUE), .groups = "drop") %>%
  arrange(desc(total)) %>%
  slice_head(n = 15) %>%
  pull(food)

tally_plot_data <- tally_data %>%
  filter(food %in% top_tally_foods) %>%
  mutate(food = factor(food, levels = top_tally_foods))
```

# Crowdsourced Cyclospora Watch

*Last updated: `r format(Sys.time(), "%B %d, %Y at %I:%M %p %Z")`*

# Feeling sick or have a confirmed case of cyclospora? [Submit your report here](https://forms.gle/QxB54kJSZV4cCFzQ6)

**`r n_total`** responses collected so far. This is a self-reported, crowdsourced
tracker built to try to spot patterns
in the current multistate cyclospora outbreak — **not** an official CDC or
state health department investigation. There is no control group, so results
below are proportional reporting among people who got sick, not proof of cause.
Treat this as "worth watching," not "confirmed."

---

# Charts

## Chart 1: Top Produce Leads by Signal Ratio

Sorted by signal ratio — how much more often cases report eating this
compared to how often people eat it in an ordinary two-week period. A ratio
above 1 means it's showing up more than you'd expect from typical diets.

```{r produce-signal-plot, fig.width=9, fig.height=6}
## Two DIFFERENT uncertainties are drawn here and they must stay visually
## distinct:
##   - dark whiskers  = 95% Wilson CI on the case proportion (sampling error)
##   - pale wide band = +/-30% on an author-estimated baseline (input error)
## A category with a sourced ERS baseline gets no pale band, which is the
## point: it makes "we guessed this denominator" visible at a glance.
produce_signal %>%
  filter(n_cases >= 3) %>%
  ggplot(aes(x = reorder(category, signal_ratio_low), y = signal_ratio)) +
  geom_linerange(aes(ymin = baseline_sens_low, ymax = baseline_sens_high),
                 linewidth = 6, colour = "#f0c9a8", na.rm = TRUE) +
  geom_col(aes(fill = signal_ratio), width = 0.62) +
  scale_fill_viridis_c(option = "inferno", guide = "none") +
  geom_errorbar(aes(ymin = signal_ratio_low, ymax = signal_ratio_high),
                width = 0.3, color = "gray30") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  coord_flip() +
  labs(title = "Produce Signal Ratio",
       subtitle = paste0("Bars = point estimate  |  dark whiskers = 95% CI on the case %  |  ",
                         "pale band = ±30% uncertainty on an estimated baseline"),
       x = NULL, y = "Signal ratio (case % / baseline %)") +
  theme_minimal(base_size = 13)
```

*See Table 1 below for the full data, including confidence intervals.*

## Chart 2: Cases by State

```{r state-map, fig.width=9, fig.height=6}
if (nrow(state_counts) > 0) {
  # Using the base "maps" package instead of usmap/sf - pure data, no
  # compiled system libraries required, so this can't break the same
  # way again. Trade-off: contiguous 48 states only (no AK/HI/DC as
  # separate shapes) - acceptable for this use case.
  us_states <- map_data("state")
  map_df <- us_states %>%
    left_join(state_counts %>% mutate(region = str_to_lower(state)), by = "region")

  ggplot(map_df, aes(long, lat, group = group, fill = n_cases)) +
    geom_polygon(color = "white", linewidth = 0.2) +
    scale_fill_viridis_c(option = "inferno", direction = -1, name = "Self-reported cases", na.value = "gray90") +
    coord_fixed(1.3) +
    theme_void() +
    labs(title = "Self-Reported Cases by State (contiguous 48 states)")
} else {
  cat("*No state data could be matched yet.*")
}
```

*This is a representation of the cases that have been self-reported in
this survey. For the official case count, please refer to the CDC or
your relevant state/local health department. See Table 2 below for the
full state-by-state count.*

## Chart 3: Cases by Canadian Province

```{r canada-map, fig.width=9, fig.height=7}
if (mapcan_available && nrow(province_counts) > 0) {
  province_shapes <- mapcan::mapcan(boundaries = province, type = standard)

  province_map_data <- province_shapes %>%
    left_join(province_counts, by = c("pr_english" = "province"))

  ggplot(province_map_data, aes(long, lat, group = group, fill = n_cases)) +
    geom_polygon(color = "white") +
    scale_fill_viridis_c(option = "inferno", direction = -1, name = "Self-reported cases", na.value = "gray90") +
    coord_fixed() +
    theme_void() +
    labs(title = "Self-Reported Cases by Province")
} else if (!mapcan_available) {
  cat("*Province map unavailable this run (mapcan package not installed).*")
} else {
  cat("*No Canadian responses yet.*")
}
```

*See Table 3 below for the full province-by-province count.*

## Chart 4: Epi Curve

```{r epi-curve, fig.width=10, fig.height=5}
if (nrow(epi_curve_data) > 0) {
  ggplot(epi_curve_data, aes(onset_date, cases)) +
    geom_col(aes(fill = cases)) +
    scale_fill_viridis_c(option = "inferno", guide = "none") +
    scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
    labs(title = "Epi Curve: Self-Reported Symptom Onset Dates",
         x = "Onset date", y = "Cases") +
    theme_minimal(base_size = 13) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
} else {
  cat("*No onset date data available yet.*")
}
```

*See Table 4 below for the full date-by-date case counts.*

## Chart 5: Reddit Thread Parsed Sources

This is a hand-compiled tally of food/restaurant mentions from Reddit threads,
kept separate from the statistical analysis above since it doesn't have the
per-person structure needed for the confidence intervals or signal ratios.
Read as "what's been mentioned together," not as a statistical finding.

```{r restaurant-food-tally, fig.width=11, fig.height=6}
if (nrow(tally_plot_data) > 0) {
  ggplot(tally_plot_data, aes(x = food, y = mentions, fill = restaurant)) +
    geom_col(position = position_dodge(preserve = "single"), color = "white", linewidth = 0.2) +
    scale_fill_viridis_d(option = "inferno") +
    theme_minimal(base_size = 12) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
    labs(title = "Reddit Mentions: Top 15 Foods by Restaurant/Source",
         x = NULL, y = "Mentions", fill = "Restaurant/Source")
} else {
  cat("*No tally data found yet - add a 'Restaurant_Food_Tally' tab to the sheet.*")
}
```

*See Table 5 below for the full mention tally (all restaurants/foods, not
just the top 15 shown here).*

---

# Data Tables

## Table 1: Produce Signal Ratio (Full Data)

```{r produce-signal-table}
## Column order here must match produce_signal's, so build the display frame
## explicitly rather than relying on however mutate() happened to order it.
produce_signal %>%
  transmute(
    category, n_cases, pct_of_cases, ci_low_pct, ci_high_pct,
    baseline_pct,
    baseline_confidence = ifelse(baseline_confidence == "exact_match",
                                 "USDA ERS", "author estimate"),
    ers_ref = ifelse(is.na(ers_ref), "—", ers_ref),
    signal_ratio, signal_ratio_low, signal_ratio_high
  ) %>%
  datatable(
    rownames = FALSE,
    colnames = c("Food", "# cases", "% of cases", "CI low", "CI high",
                 "Baseline % (used in ratio)", "Baseline source",
                 "ERS reference (not used in ratio)",
                 "Signal ratio", "Ratio CI low", "Ratio CI high"),
    options = list(pageLength = 10, order = list(list(8, "desc")), scrollX = TRUE))
```

*CI columns are a 95% confidence interval — small sample sizes mean wide
ranges. If the "Ratio CI low" column is still above 1, that's a stronger
lead than the point estimate alone.*

### Where these baselines come from

The signal ratio divides how often cases report a food by a **baseline** —
how commonly people eat it normally. That denominator drives every number
in this table, so it's worth being explicit about where it comes from.

```{r baseline-provenance-note, results="asis"}
cat(sprintf(
"Of the %d foods below, **%d have a baseline sourced from USDA ERS** and
**%d rest on the author's own estimate**. Both are labeled in the
\"Baseline source\" column.\n\n", n_ers_sourced + n_estimated, n_ers_sourced, n_estimated))
```

- **Author estimates** are exactly that — considered guesses, not
  measurements, and not derived from any survey. They carry a **pale ±30%
  band** on the chart above to show roughly how much the ratio would move if
  the guess were off by that much. The band is one flat width for every
  estimate; pretending to know which guesses are shakier than others would
  be false precision.
- **USDA ERS** values come from the
  [Food Availability (Per Capita) Data System](https://www.ers.usda.gov/data-products/food-availability-per-capita-data-system),
  refreshed monthly into `baselines-external.json`.

**The ERS column is shown but not yet used**, and the reason is a real
limitation rather than an oversight. ERS publishes *pounds of food available
per person per year*; the baseline this ratio needs is *the share of people
who ate a food in a two-week window*. Those measure different things and
cannot be converted into one another — 19 lb of tomatoes a year could be
everyone eating a little or a few people eating a lot. Substituting one for
the other would change every ratio on this page for no reason but a change
of units. Reconciling them properly is open work; until then both numbers
are shown side by side so the gap is visible rather than hidden.

Foods without any baseline at all don't appear in this table — they're still
counted in *All produce mentioned* further down.

## Table 2: Cases by State (Full Data)

```{r state-table}
if (nrow(state_counts) > 0) {
  datatable(state_counts, rownames = FALSE,
            colnames = c("State", "# cases"),
            options = list(pageLength = 10))
} else {
  cat("*No state data available yet.*")
}
```

## Table 3: Cases by Canadian Province (Full Data)

```{r province-table}
if (nrow(province_counts) > 0) {
  datatable(province_counts, rownames = FALSE,
            colnames = c("Province", "# cases"),
            options = list(pageLength = 10))
} else {
  cat("*No Canadian responses yet.*")
}
```

## Table 4: Epi Curve Data (Full Data)

```{r epi-curve-table}
if (nrow(epi_curve_data) > 0) {
  datatable(epi_curve_data, rownames = FALSE,
            colnames = c("Onset date", "Cases"),
            options = list(pageLength = 10))
} else {
  cat("*No onset date data available yet.*")
}
```

## Table 5: Reddit Mention Tally (Full Data)

```{r tally-table}
if (nrow(tally_data) > 0) {
  datatable(tally_data %>% arrange(desc(mentions)), rownames = FALSE,
            colnames = c("Restaurant/Source", "Food", "Mentions"),
            options = list(pageLength = 10))
} else {
  cat("*No tally data found yet - add a 'Restaurant_Food_Tally' tab to the sheet.*")
}
```

## Table 6: All Produce Mentioned

```{r produce-table}
datatable(produce_freq, rownames = FALSE,
          colnames = c("Food", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Table 7: Stores & Restaurants Mentioned

```{r store-table}
datatable(store_freq, rownames = FALSE,
          colnames = c("Store/restaurant", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Table 8: Reported Symptom Duration

Cyclospora illness tends to run longer than most foodborne bugs (often weeks,
sometimes relapsing). Short-duration reports are more likely something else.

```{r duration-table}
if (nrow(duration_summary) > 0) {
  datatable(duration_summary, rownames = FALSE,
            colnames = c("Duration", "# responses", "% of responses"),
            options = list(pageLength = 10))
}
```

---

**How to read this page:** a high signal ratio means the food is reported by
sick people more than you'd expect from normal eating habits — that's a lead
worth watching, not a verdict. Small numbers (a food only 2-3 people
mentioned) are noisy and easy to over-read. If something looks concerning and
consistent, the right next step is reporting it to your **local or state
health department**, who can do formal case-control interviews and trace
product lots — this page can't do that part.

*Want to add your own report? [Fill out the form here](https://forms.gle/6zFfhiaGcw7xHDKa7).*

```{r persist-vocabulary}
# Persist the (possibly grown) vocabulary so the next scheduled run reuses
# these categories instead of starting over. The GitHub Action commits this
# file alongside index.html.
#
# This runs LAST, deliberately. Every chart and table above has already
# rendered by now, so an interrupted or failed render can never leave a
# written vocabulary behind with no corresponding page. save_vocabulary()
# re-reads and merges before writing, so this is safe even if another run
# has touched the file while this one was rendering.
#
# Integrity is checked HERE rather than next to stamp_category_provenance(),
# because that runs before the store classification and so cannot see
# categories minted by it. This is the only point where every route that can
# add a category has finished.
vocab <- check_vocabulary_integrity(vocab)
save_vocabulary(vocab, VOCAB_PATH)

# Record what this run actually produced, so the publishing workflow can refuse
# to commit a degraded page. Written last, alongside the vocabulary, for the
# same reason: an interrupted render leaves neither. index_html_bytes reads 0
# here because pandoc has not written the file yet - the workflow fills it in
# after rendering. See scripts/check-render.R.
write_run_manifest(build_run_manifest(
  n_responses                 = n_total,
  produce_categories_reported = nrow(produce_freq),
  store_categories_reported   = nrow(store_freq),
  vocab                       = vocab,
  classification_method       = CLASSIFICATION_METHOD,
  events                      = classification_events()
))
```
