---
title: "Crowdsourced Cyclospora Watch"
output:
  html_document:
    theme: flatly
    toc: false
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

required_pkgs <- c("googlesheets4", "dplyr", "tidyr", "stringr", "lubridate",
                    "ggplot2", "janitor", "purrr", "knitr", "DT", "httr2", "jsonlite", "usmap")
new_pkgs <- required_pkgs[!(required_pkgs %in% installed.packages()[, "Package"])]
if (length(new_pkgs)) install.packages(new_pkgs)
library(googlesheets4); library(dplyr); library(tidyr); library(stringr)
library(lubridate); library(ggplot2); library(janitor); library(purrr)
library(knitr); library(DT)
```

```{r config}
# ---- EDIT THIS SECTION FOR YOUR FORM ----
SHEET_URL <- "https://docs.google.com/spreadsheets/d/1n1VJ99Ko7mvFQmKRX_QrFLFFziMAGKpkUNmK40QxLpU/edit?usp=sharing"
gs4_deauth()

col_signatures <- c(
  timestamp        = "^timestamp$",
  consent          = "consent",
  state            = "what state",
  why_believe      = "why do you believe",
  produce_checklist = "did you eat any of the following",
  produce_other    = "anything else you remember eating",
  shop_raw         = "shop.?dine",
  duration         = "how long did symptoms last",
  onset_date       = "when did symptoms start"
)

match_columns <- function(actual_names, signatures) {
  matched <- vapply(signatures, function(sig) {
    hits <- actual_names[str_detect(str_to_lower(actual_names), str_to_lower(sig))]
    if (length(hits) == 0) NA_character_ else hits[1]
  }, character(1))
  matched[!is.na(matched)]
}

# Seed dictionaries - starting point + offline fallback only. The real,
# growing vocabulary lives in category_vocabulary.json (see below).
produce_dict_seed <- list(
  lettuce = "lettuce|romaine|iceberg|spring mix|spinach mix|leafy green",
  spinach = "spinach", cilantro = "cilantro|coriander", basil = "\\bbasil\\b",
  parsley = "parsley", raspberries = "raspberr", strawberries = "strawberr",
  blackberries = "blackberr", cucumber = "cucumber", tomato = "tomato",
  snap_peas = "snap pea|sugar snap", green_onion = "green onion|scallion|spring onion",
  cabbage = "cabbage|slaw", carrot = "carrot", broccoli = "broccoli",
  melon = "cantaloupe|honeydew|melon", bell_pepper = "bell pepper|sweet pepper",
  avocado = "avocado|guacamole", celery = "celery", cauliflower = "cauliflower",
  dill = "\\bdill\\b", radish = "radish",
  mint = "\\bmint\\b", salad_bagged = "bagged salad|salad kit|salad mix",
  salad_restaurant = "restaurant salad|salad bar"
)

store_dict_seed <- list(
  kroger = "kroger", trader_joes = "trader joe", whole_foods = "whole foods",
  walmart = "wal[- ]?mart", target = "\\btarget\\b", publix = "publix",
  aldi = "aldi", costco = "costco", safeway = "safeway", wegmans = "wegmans",
  taco_bell = "taco bell", chipotle = "chipotle", subway = "subway",
  mcdonalds = "mcdonald", local_farmers_market = "farmers?[- ]?market",
  local_restaurant = "^restaurant$|local restaurant"
)

baseline_commonness_seed <- c(
  lettuce = 55, spinach = 25, cilantro = 20, basil = 10, parsley = 12,
  raspberries = 10, strawberries = 30, blackberries = 8, cucumber = 30,
  tomato = 45, snap_peas = 8, green_onion = 20, cabbage = 15, carrot = 40,
  broccoli = 35, melon = 20, bell_pepper = 30, avocado = 35, celery = 15,
  cauliflower = 15, dill = 8,
  radish = 6, mint = 5, salad_bagged = 25, salad_restaurant = 20
)

VOCAB_PATH <- "category_vocabulary.json"

load_vocabulary <- function(path, seed_produce, seed_store, seed_baseline) {
  v <- if (file.exists(path)) tryCatch(jsonlite::fromJSON(path, simplifyVector = TRUE), error = function(e) NULL) else NULL
  list(
    produce_categories = union(if (!is.null(v)) v$produce_categories else character(0), seed_produce),
    store_categories   = union(if (!is.null(v)) v$store_categories else character(0), seed_store),
    baseline_commonness = modifyList(
      as.list(seed_baseline),
      if (!is.null(v) && !is.null(v$baseline_commonness)) as.list(v$baseline_commonness) else list()
    ),
    # PERSISTENT CLASSIFICATION CACHE - locks in each specific raw phrase's
    # decision forever, so already-classified responses can't silently
    # drift to a different category on a later run.
    produce_item_map = if (!is.null(v) && !is.null(v$produce_item_map)) as.list(v$produce_item_map) else list(),
    store_item_map    = if (!is.null(v) && !is.null(v$store_item_map)) as.list(v$store_item_map) else list()
  )
}

save_vocabulary <- function(vocab, path) {
  jsonlite::write_json(vocab, path, auto_unbox = TRUE, pretty = TRUE)
}
```

```{r functions}
split_freetext <- function(raw_text_vec) {
  tibble(row_id = seq_along(raw_text_vec), raw = raw_text_vec) %>%
    filter(!is.na(raw), str_trim(raw) != "") %>%
    separate_rows(raw, sep = ",") %>%
    mutate(item = str_trim(str_to_lower(raw))) %>%
    filter(item != "")
}

regex_classify <- function(item, dict) {
  hit <- names(dict)[map_lgl(dict, ~ str_detect(item, .x))]
  if (length(hit) == 0) return(str_to_title(item))
  hit[1]
}

# LLM does the primary classification and grows the category vocabulary -
# reuses existing categories where they fit, mints new lowercase_snake_case
# ones for genuinely new foods instead of dumping them in "other". Falls
# back to regex automatically if the API call fails.
CLASSIFICATION_METHOD <- "llm"   # "llm" or "regex"

call_claude_classify_dynamic <- function(items, known_categories, domain = c("produce", "store"),
                                          api_key = Sys.getenv("ANTHROPIC_API_KEY"),
                                          model = "claude-haiku-4-5-20251001") {
  domain <- match.arg(domain)
  if (identical(api_key, "") || length(items) == 0) return(NULL)

  domain_instructions <- if (domain == "produce") {
    paste0(
      "1. If it clearly matches an EXISTING category, use that EXACT category name - do not ",
      "create a near-duplicate or synonym (e.g. don't make \"fresh_cilantro\" if \"cilantro\" ",
      "already exists).\n",
      "2. If it genuinely doesn't fit any existing category, invent ONE new concise category ",
      "name in lowercase_snake_case (1-3 words, e.g. \"purslane\" or \"bean_sprouts\") that ",
      "could sensibly apply to future similar items too. Do NOT use \"other\" - always pick or ",
      "create a real, specific category.\n",
      "3. If multiple items in this batch describe the same new food, give them the SAME new ",
      "category name.\n"
    )
  } else {
    paste0(
      "1. Your ONLY job is to normalize SPELLING/PHRASING variants of the SAME specific named ",
      "place into one category (e.g. \"Krogers\", \"the kroger on main\", \"kroger grocery\" all ",
      "become \"kroger\"). If an EXISTING category is clearly the same specific place, use that ",
      "EXACT category name.\n",
      "2. NEVER invent a generic business-type category like \"regional_grocery\", ",
      "\"casual_dining\", \"fast_casual\", \"grocery_store\", or \"local_restaurant\" - these hide ",
      "the actual place and are USELESS for a foodborne illness traceback, which requires ",
      "knowing exactly which specific establishment was involved.\n",
      "3. If the item names any identifiable specific business, chain, or restaurant (even a ",
      "small independent one you don't otherwise know), use a lowercase_snake_case version of ",
      "THAT EXACT NAME as the category (e.g. \"harris_teeter\", \"joes_pizza_downtown\"). Do not ",
      "abstract it into a category of business.\n",
      "4. ONLY if the respondent's answer truly contains NO identifiable name at all (e.g. they ",
      "wrote just \"a restaurant\" or \"the grocery store\" with zero distinguishing details) use ",
      "exactly \"unspecified_restaurant\" or \"unspecified_grocery_store\" - do not invent any ",
      "other generic bucket beyond these two exact fallback labels.\n"
    )
  }

  prompt <- paste0(
    "You are maintaining a GROWING category taxonomy for a citizen-science foodborne ",
    "illness investigation. Respondents write vague, hedged, or typo'd free text.\n\n",
    "Categories that ALREADY EXIST: ", paste(known_categories, collapse = ", "), "\n\n",
    "For each item below:\n",
    domain_instructions, "\n",
    "Respond with ONLY a raw JSON object mapping each exact input item (as written, as the ",
    "key) to its category (as the value). No prose, no markdown code fences.\n\nItems:\n",
    paste0("- ", items, collapse = "\n")
  )
  resp <- tryCatch({
    httr2::request("https://api.anthropic.com/v1/messages") %>%
      httr2::req_headers("x-api-key" = api_key, "anthropic-version" = "2023-06-01",
                          "content-type" = "application/json") %>%
      httr2::req_body_json(list(model = model, max_tokens = 4096,
                                 messages = list(list(role = "user", content = prompt)))) %>%
      httr2::req_perform()
  }, error = function(e) NULL)
  if (is.null(resp)) return(NULL)
  text_out <- str_remove_all(httr2::resp_body_json(resp)$content[[1]]$text, "```json|```")
  tryCatch(jsonlite::fromJSON(text_out), error = function(e) NULL)
}

classify_items_dynamic <- function(items, known_categories, dict, domain = c("produce", "store"), method = c("llm", "regex")) {
  domain <- match.arg(domain)
  method <- match.arg(method)
  if (length(items) == 0) return(list(mapping = character(0), vocab = known_categories))
  if (method == "regex") {
    mapping <- setNames(map_chr(items, ~ regex_classify(.x, dict)), items)
    return(list(mapping = mapping, vocab = union(known_categories, unique(mapping))))
  }
  result <- call_claude_classify_dynamic(items, known_categories, domain = domain)
  if (is.null(result) || length(result) == 0) {
    mapping <- setNames(map_chr(items, ~ regex_classify(.x, dict)), items)
    return(list(mapping = mapping, vocab = union(known_categories, unique(mapping))))
  }
  mapping <- unlist(result)[items]
  mapping <- str_replace_all(str_to_lower(str_trim(mapping)), "[^a-z0-9]+", "_")
  mapping <- str_replace_all(mapping, "^_|_$", "")
  names(mapping) <- items
  missing <- is.na(mapping) | mapping == ""
  if (any(missing)) mapping[missing] <- map_chr(items[missing], ~ regex_classify(.x, dict))
  list(mapping = mapping, vocab = union(known_categories, unique(mapping)))
}

## Classifies free text AND grows the vocabulary in one step - CACHE-FIRST:
## any raw phrase already decided in a previous run gets its locked-in
## answer from item_map, no LLM call, no chance of drifting to a
## different answer. Only phrases genuinely never seen before go to the
## LLM, and that one-time decision gets saved into item_map permanently.
classify_and_grow <- function(raw_text_vec, known_categories, item_map, dict, domain = "produce", method = "llm") {
  long <- split_freetext(raw_text_vec)
  if (nrow(long) == 0) return(list(long = long %>% mutate(category = character(0)), vocab = known_categories, item_map = item_map))

  distinct_items <- unique(long$item)

  cached_category <- vapply(distinct_items, function(it) {
    val <- item_map[[it]]
    if (is.null(val)) NA_character_ else as.character(val)
  }, character(1))
  names(cached_category) <- distinct_items

  uncached_items <- distinct_items[is.na(cached_category)]

  if (length(uncached_items) > 0) {
    result <- classify_items_dynamic(uncached_items, known_categories, dict, domain = domain, method = method)
    known_categories <- result$vocab
    cached_category[uncached_items] <- result$mapping[uncached_items]
    for (it in uncached_items) item_map[[it]] <- unname(cached_category[[it]])
  }

  list(
    long = long %>% mutate(category = unname(cached_category[item])),
    vocab = known_categories,
    item_map = item_map
  )
}
```

```{r load-data}
raw <- read_sheet(SHEET_URL)
present_map <- match_columns(names(raw), col_signatures)

df <- raw %>%
  select(all_of(unname(present_map))) %>%
  rename(!!!present_map) %>%
  clean_names() %>%
  mutate(response_id = row_number())

if ("consent" %in% names(df)) {
  df <- df %>%
    filter(str_detect(str_to_lower(str_trim(as.character(consent))), "^yes"))
}

n_total <- nrow(df)

duration_summary <- if ("duration" %in% names(df)) {
  df %>%
    count(duration, sort = TRUE, name = "n_responses") %>%
    mutate(pct = round(100 * n_responses / n_total, 1))
} else tibble()

vocab <- load_vocabulary(VOCAB_PATH, names(produce_dict_seed), names(store_dict_seed), baseline_commonness_seed)

produce_combined <- if (all(c("produce_checklist", "produce_other") %in% names(df))) {
  paste(coalesce(as.character(df$produce_checklist), ""), coalesce(as.character(df$produce_other), ""), sep = ", ")
} else if ("produce_checklist" %in% names(df)) {
  df$produce_checklist
} else if ("produce_other" %in% names(df)) {
  df$produce_other
} else {
  NULL
}

if (!is.null(produce_combined)) {
  produce_result <- classify_and_grow(produce_combined, vocab$produce_categories, vocab$produce_item_map, produce_dict_seed, domain = "produce", method = CLASSIFICATION_METHOD)
  produce_long <- produce_result$long %>% mutate(response_id = row_id, .keep = "unused")
  vocab$produce_categories <- produce_result$vocab
  vocab$produce_item_map <- produce_result$item_map
} else {
  produce_long <- tibble()
}

if ("shop_raw" %in% names(df)) {
  store_result <- classify_and_grow(df$shop_raw, vocab$store_categories, vocab$store_item_map, store_dict_seed, domain = "store", method = CLASSIFICATION_METHOD)
  store_long <- store_result$long %>% mutate(response_id = row_id, .keep = "unused")
  vocab$store_categories <- store_result$vocab
  vocab$store_item_map <- store_result$item_map
} else {
  store_long <- tibble()
}

# Persist the (possibly grown) vocabulary so the next scheduled run reuses
# these categories instead of starting over. The GitHub Action commits this
# file alongside index.html.
save_vocabulary(vocab, VOCAB_PATH)

# 95% Wilson score CI on each proportion - stays sane at small n and near
# 0%/100%, unlike the naive normal approximation. Base R only.
wilson_ci <- function(x, n, conf_level = 0.95) {
  if (n == 0) return(c(lower = NA_real_, upper = NA_real_))
  p_hat <- x / n
  z <- qnorm(1 - (1 - conf_level) / 2)
  denom <- 1 + z^2 / n
  center <- p_hat + z^2 / (2 * n)
  adj <- z * sqrt((p_hat * (1 - p_hat) + z^2 / (4 * n)) / n)
  c(lower = max(0, (center - adj) / denom), upper = min(1, (center + adj) / denom))
}

add_wilson_ci <- function(freq_df, n_total) {
  ci <- purrr::map2_dfr(freq_df$n_cases, n_total, ~ as.list(wilson_ci(.x, .y)))
  freq_df %>%
    mutate(ci_low_pct = round(ci$lower * 100, 1), ci_high_pct = round(ci$upper * 100, 1))
}

produce_freq <- produce_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

store_freq <- store_long %>%
  distinct(response_id, category) %>%
  count(category, sort = TRUE, name = "n_cases") %>%
  mutate(pct_of_cases = round(100 * n_cases / n_total, 1)) %>%
  add_wilson_ci(n_total)

produce_signal <- produce_freq %>%
  mutate(baseline_pct = unlist(vocab$baseline_commonness)[category]) %>%
  filter(!is.na(baseline_pct)) %>%
  mutate(
    signal_ratio = round(pct_of_cases / baseline_pct, 2),
    signal_ratio_low = round(ci_low_pct / baseline_pct, 2),
    signal_ratio_high = round(ci_high_pct / baseline_pct, 2)
  ) %>%
  # Sort by conservative lower-bound ratio, not the raw point estimate -
  # discounts small-n flukes, rewards foods elevated even pessimistically.
  arrange(desc(signal_ratio_low), desc(signal_ratio))
```

# Crowdsourced Cyclospora Watch

*Last updated: `r format(Sys.time(), "%B %d, %Y at %I:%M %p %Z")`*

# Feeling sick or have a confirmed case of cyclospora? [Submit your report here](https://forms.gle/QxB54kJSZV4cCFzQ6)

**`r n_total`** responses collected so far. This is a self-reported, crowdsourced
tracker meant to try to spot patterns
in the current multistate cyclospora outbreak — **not** an official CDC or
state health department investigation. There is no control group, so results
below are proportional reporting among people who got sick, not proof of cause.
Treat this as "worth watching," not "confirmed."

## Top produce leads

Sorted by signal ratio — how much more often cases report eating this
compared to how often people eat it in an ordinary two-week period. A ratio
above 1 means it's showing up more than you'd expect from typical diets.

```{r produce-signal-table}
datatable(produce_signal, rownames = FALSE,
          colnames = c("Food", "# cases", "% of cases", "CI low", "CI high", "Baseline %",
                       "Signal ratio", "Ratio CI low", "Ratio CI high"),
          options = list(pageLength = 10, order = list(list(7, "desc"))))
```

*CI columns are a 95% confidence interval — small sample sizes mean wide
ranges. If the "Ratio CI low" column is still above 1, that's a stronger
lead than the point estimate alone.*

```{r produce-signal-plot, fig.width=9, fig.height=6}
produce_signal %>%
  filter(n_cases >= 3) %>%
  ggplot(aes(x = reorder(category, signal_ratio_low), y = signal_ratio)) +
  geom_col(fill = "#c0392b") +
  geom_errorbar(aes(ymin = signal_ratio_low, ymax = signal_ratio_high), width = 0.3, color = "gray30") +
  geom_hline(yintercept = 1, linetype = "dashed", color = "gray40") +
  coord_flip() +
  labs(title = "Produce Signal Ratio", subtitle = "Bars = point estimate, whiskers = 95% CI",
       x = NULL, y = "Signal ratio (case % / baseline %)") +
  theme_minimal(base_size = 13)
```

## All produce mentioned

```{r produce-table}
datatable(produce_freq, rownames = FALSE,
          colnames = c("Food", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Cases by state

```{r state-map, fig.width=9, fig.height=6}
if ("state" %in% names(df)) {
  normalize_state <- function(x) {
    x <- str_trim(x)
    full_match <- state.name[match(str_to_title(x), state.name)]
    abbr_match <- state.name[match(str_to_upper(x), state.abb)]
    dc_match <- ifelse(
      str_to_lower(x) %in% c("dc", "washington dc", "washington, dc", "district of columbia"),
      "District of Columbia", NA_character_
    )
    coalesce(full_match, abbr_match, dc_match)
  }

  state_counts <- df %>%
    mutate(state = normalize_state(state)) %>%
    filter(!is.na(state)) %>%
    count(state, name = "n_cases")

  if (nrow(state_counts) > 0) {
    usmap::plot_usmap(data = state_counts, values = "n_cases", color = "white") +
      scale_fill_continuous(low = "#fde8e6", high = "#c0392b", name = "Self-reported cases", na.value = "gray95") +
      theme(legend.position = "right") +
      labs(title = "Self-Reported Cases by State")
  } else {
    cat("*No state data could be matched yet.*")
  }
}
```

*This is a representation of the cases that have been self-reported in
this survey. For the official case count, please refer to the CDC or
your relevant state/local health department.*

## Stores & restaurants mentioned

```{r store-table}
datatable(store_freq, rownames = FALSE,
          colnames = c("Store/restaurant", "# cases", "% of cases", "CI low", "CI high"),
          options = list(pageLength = 10))
```

## Reported symptom duration

Cyclospora illness tends to run longer than most foodborne bugs (often weeks,
sometimes relapsing). Short-duration reports are more likely something else.

```{r duration-table}
if (nrow(duration_summary) > 0) {
  datatable(duration_summary, rownames = FALSE,
            colnames = c("Duration", "# responses", "% of responses"),
            options = list(pageLength = 10))
}
```

## Epi curve

```{r epi-curve, fig.width=10, fig.height=5}
if ("onset_date" %in% names(df)) {
  epi_curve_data <- df %>%
    mutate(onset_date = suppressWarnings(
      lubridate::parse_date_time(onset_date,
        orders = c("mdy", "ymd", "dmy", "mdY HMS", "ymd HMS"))
    )) %>%
    mutate(onset_date = as_date(onset_date)) %>%
    filter(!is.na(onset_date)) %>%
    count(onset_date, name = "cases")

  if (nrow(epi_curve_data) > 0) {
    ggplot(epi_curve_data, aes(onset_date, cases)) +
      geom_col(fill = "#c0392b") +
      scale_x_date(date_breaks = "1 week", date_labels = "%b %d") +
      labs(title = "Epi Curve: Self-Reported Symptom Onset Dates",
           x = "Onset date", y = "Cases") +
      theme_minimal(base_size = 13) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
  }
}
```

---

**How to read this page:** a high signal ratio means the food is reported by
sick people more than you'd expect from normal eating habits — that's a lead
worth watching, not a verdict. Small numbers (a food only 2-3 people
mentioned) are noisy and easy to over-read. If something looks concerning and
consistent, the right next step is reporting it to your **local or state
health department**, who can do formal case-control interviews and trace
product lots — this page can't do that part.

*Want to add your own report? [Fill out the form here](https://forms.gle/6zFfhiaGcw7xHDKa7).*
